Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-10-08 paper.tex
edited dataset paragraph

        As we wish to evaluate and compare scientific workflow frameworks with
        Big Data frameworks for the processing of neuroimaging big data, we will
        break down our analyses by the four principal features necessary for
        effective neuroimaging workflow engines. The workflow engines discussed
        will include SPM, LONI, Nipype, PSOM, FastR, AA, Pydpiper 
        for neuroimaging; Taverna, Pegasus, Make, OpenMOLE, Nextflow, Galaxy, 
        Toil for other scientific workflows; and MapReduce, Spark and Dask for
        Big Data Frameworks. Chapter \ref{workcomp} will evaluate these 
        workflows on the basis of workflow composition: we will % 'in other words' is on my list of expressions to avoid
        examine the programming languages necessary to construct these workflows
        , how easy is it to add new tools and will these workflows be understood
        by the community. In Chapter \ref{performance}, we will proceed to 
        investigate the strategies employed by these frameworks to improve the 
        performance of their workflows. Chapter \ref{portability} will discuss
        the portability of the workflows written using these frameworks. 
        Workflow reproducibility will be then discussed in Chapter 
        \ref{reproducibility}.

@@

            As a result of the rise in data sharing in neuroscience, neuroimaging
            Big Data has come to fruition. The field of neuroscience has now
            reached a bottleneck where there exists sufficient data to make
            impactful studies, but the software to process these datasets have 
            not evolved with the size of the data.

            Neuroimaging big data comes in two formats: 1) large images and 2) 
            large datasets. Large images consist of singular images ranging 
            from 100s of gigabytes to terabytes in size. A well-known example of 
            such an image is the BigBrain \note{cite here}, a histological image 
            of the brain of a healthy 69 year-old man. At its highest resolution
            , it is 1x1x20$\mu$m or 1TB in
            size. Other examples of large images can be found in electron 
            microscopy (EM), polarized light imaging (PLI) and micro computational
            tomography (microCT) \note{need to do more research here.cite}. 
            Images at 
            such high resolution are important to researchers as they provide 
            insights into aspects not otherwise detectible in images at lower 
            resolutions. However, due to their size and lack of resources 
            available to process such images, research on this data remains 
            limited.

            In contrast, large datasets consist of many images acquired from
            multiple subjects, which are too large to be processed in their
            entirety. Notable examples of these datasets include the 
            Alzheimer's Disease Neuroimaging Initiative (ADNI), OpenfMRI, 
            the Autism Brain Imaging Data Exchange (ABIDE), the Consortium for
            Reliability and Reproducibility (CoRR), the Human Connectome Project
            (HCP) and the UK Biobank, with the later
            two being flagship recent examples of large datasets in neuroimaging.

@@

            ABIDE was conceived to promote the advancement of knowledge 
            of Autism Spectrum Disorders (ASD). % inverted the sentence to keep symmetry with the other paragraphs
            ABIDE is an open repository of 
            preprocessed data obtained from 1112 R-fMRI datasets.
            In addition to R-fMRI, datasets also contain the corresponding 
            structural MRI and phenotypic data. As data made available in ABIDE
            is preprocessed, standardized pipelines were developed for the 
            preprocessing of the images. Popular neuroimaging processing tools
            such as CIVET, ANTs, and FreeSurfer \note{cite} were used for the 
            preprocessing of structural data, and several other pipelines were
            used for the processing of functional data.

            The CoRR \tristan{expand acronym} was developed as an initiative to study and improve the 
            reliability and reproducibility of functional connectomics. The 
            data made available by the Consortium consists of test-retest data 
            obtained from 33 datasets. The repository contains data from 1629 
            subjects, in which anatomical, R-fMRI, dMRI, CBF and ASL scans are 
            available \note{obtained from website}.

@@

            All these initiative stress the importance of data-sharing and
            large-scale studies for the advancement of science. Many researchers
            are limited to the processing of subsets of the data available as 
            they lack compute and storage resources to process the data in its
            entirety. It is also important to note that many of the pipelines 
            developed by these initiatives made use of popular neuroimaging 
            toolboxes, such as FSL, FreeSurfer, ANTS, CIVET, rather that
            creating their own. Therefore, there is a great need for Big Data
            frameworks that can leverage existing tools for the efficient 
            processing of large-scale datasets. With the availability of such 
            tools, many more research labs will be able to perform
            higher-impact studies \note{reword}.

>>>>

        As we wish to evaluate and compare scientific workflow frameworks with
        Big Data frameworks for the processing of neuroimaging big data, we will
        break down our analyses by the four principal features necessary for
        effective neuroimaging workflow engines. The workflow engines discussed
        will include SPM, LONI, Nipype, PSOM, FastR, AA, Pydpiper 
        for neuroimaging; Taverna~\cite{doi:10.1093/bioinformatics/bth361}, 
        Pegasus, Make~\cite{10.3389/fninf.2016.00002}, 
        OpenMOLE~\cite{passerat2014openmole}, Nextflow~\cite{Di-Tommaso:2017aa}
        , Galaxy~\cite{Goecks2010}, 
        Toil for other scientific workflows; and Hadoop 
        MapReduce~\cite{Dean:2008:MSD:1327452.1327492}, Spark and Dask for
        Big Data Frameworks. Chapter \ref{workcomp} will evaluate these 
        workflows on the basis of workflow composition: we will % 'in other words' is on my list of expressions to avoid
        examine the programming languages necessary to construct these workflows
        , as well as, how easy is it to add new tools. In Chapter 
        \ref{performance}, we will proceed to 
        investigate the strategies employed by these frameworks to improve the 
        performance of their workflows. Chapter \ref{portability} will discuss
        the portability of the workflows written using these frameworks. 
        Workflow reproducibility will be then discussed in Chapter 
        \ref{reproducibility}.

@@

            As a result of the rise in data sharing in neuroscience, 
            neuroimaging
            BigData has come to fruition. The field of neuroscience has now
            reached a bottleneck where there exists sufficient data to make
            impactful studies, but the software to process these datasets have 
            not evolved with the size of the data.

            Neuroimaging big data comes in two formats: 1) large images and 2) 
            large datasets. Large images consist of singular images ranging 
            from 100s of gigabytes to terabytes in size. A well-known example 
            of 
            such an image is the BigBrain~\cite{Amunts1472}, a histological 
            image 
            of the brain of a healthy 69 year-old man. At its highest resolution
            , it is 1x1x20$\mu$m or 1TB in
            size. Other examples of large images can be found in electron 
            microscopy (EM)~\cite{Hildebrand:2017aa}, polarized light imaging 
            (PLI)~\cite{10.1007/978-3-319-12084-3_1} and micro computational
            tomography (microCT)~\cite{10.1371/journal.pone.0035691}. 
            Images at 
            such high resolution are important to researchers as they provide 
            insights into aspects not otherwise detectible in images at lower 
            resolutions. However, due to their size and lack of resources 
            available to process such images, research on this data remains 
            limited.

            In contrast, large datasets consist of many images acquired from
            multiple subjects, which are too large to be processed in their
            entirety. Notable examples of these datasets include the 
            Alzheimer's Disease Neuroimaging Initiative 
            (ADNI)~\cite{doi:10.1002/jmri.21049}, 
            OpenfMRI~\cite{POLDRACK2017259}, 
            the Autism Brain Imaging Data Exchange 
            (ABIDE)~\cite{Di-Martino:2013aa}, the Consortium for
            Reliability and Reproducibility (CoRR)~\cite{Zuo:2014aa}, the Human 
            Connectome Project (HCP)~\cite{VANESSEN201362} and the UK 
            Biobank~\cite{Miller:2016aa}, with the later
            two being flagship recent examples of large datasets in 
            neuroimaging.

@@

            ABIDE was conceived to promote the advancement of knowledge 
            of Autism Spectrum Disorders (ASD). % inverted the sentence to keep symmetry with the other paragraphs
            ABIDE is an open repository of 
            preprocessed data obtained from 1112 R-fMRI datasets.
            In addition to R-fMRI, datasets also contain the corresponding 
            structural MRI and phenotypic data. As data made available in ABIDE
            is preprocessed, standardized pipelines were developed for the 
            preprocessing of the images. Popular neuroimaging processing tools
            such as CIVET~\cite{citation-0}, ANTs~\cite{avants2009advanced}, 
            and FreeSurfer~\cite{FISCHL2012774} were used for the 
            preprocessing of structural data, and several other pipelines were
            used for the processing of functional data.

            The Consortium for Reliability and Reproducibility 
            \tristan{expand acronym} was developed as an initiative to study 
            and improve the 
            reliability and reproducibility of functional connectomics. The 
            data made available by the Consortium consists of test-retest data 
            obtained from 33 datasets. The repository contains data from 1629 
            subjects, in which anatomical, R-fMRI, dMRI, CBF and ASL scans are 
            available \note{obtained from website}.

@@

            All these initiative stress the importance of data-sharing and
            large-scale studies for the advancement of science. Many researchers
            are limited to the processing of subsets of the data available as 
            they lack compute and storage resources to process the data in its
            entirety. It is also important to note that many of the pipelines 
            developed by these initiatives made use of popular neuroimaging 
            toolboxes, such as FSL~\cite{SMITH2004S208}, FreeSurfer, ANTS, 
            CIVET, rather than
            creating their own. Therefore, there is a great need for Big Data
            frameworks that can leverage existing tools for the efficient 
            processing of large-scale datasets. Widespread availability and 
            accessibility of such frameworks will in turn lead to a greater
            volume of higher-impact studies.
